Supplemental Material for\\Evaluating `Graphical Perception' with CNNs

### 2018-03-31 PAPER/06_bars_and_framed_rectangles_experiment.tex

>>>>

\begin{figure}[t]
	  \includegraphics[width=\linewidth]{weber_mlae_noise_all.pdf}
  \caption{\textbf{Computational results of the Weber-Fechner's Law experiment.} Log absolute error means and 95\% confidence intervals for the \emph{bars-and-framed-rectangles experiment} as described by Cleveland and McGill~\cite{cleveland_mcgill}. We test the performance of a Multi-layer Perceptron (MLP), the LeNet Convolutional Neural Network, as well as feature generation using the VGG19 and Xception networks trained on ImageNet.}
	\label{fig:weber_law}
\end{figure}

### 2018-03-31 PAPER/SUPPLEMENTAL/supplemental.tex

>>>>

\begin{figure}[p]
	\centering
	  \includegraphics[width=\linewidth]{../gfx/weber_training_loss_all.pdf}
	  \includegraphics[width=\linewidth]{../gfx/weber_validation_loss_all.pdf}
  \caption{\textbf{Loss plots for the weber-fechner's law experiment including VGG19 and Xception.} We visualize the MSE loss on training data and for unseen validation data after each epoch. This plot includes the VGG19 and Xception networks trained from scratch.}
	\label{fig:weber_loss_all}
\end{figure}
